### 2014-05-21 paper.draft.tex
paper draft

Geographic Layout techniques are very effective for building overlays with a 
high degree of physical locality. However, we found that in the context of 
community networks it may not be the best choice. Network splits are common due to both, 
hardware malfunction (low-end hardware used) and humman errors during management 
operations (difficulty of operating a highly descentralized network). Because of network 
splits a perfect locality may lead to entire portions of the DHT ID space inaccessible. 
In this sense, Proximity Routing and Proximity Neighbour Selection provides much better 
reliability since the Node IDs have nothing to do with the geographic location.

@@

We believe that Proximity Neighbour Selection offers the best characteristics for 
deployment on CN. ID space is uniformly distributed over the whole network, making 
it robust, while good enough locality can still be achieved by choosing good candidates 
as routing table entries.

>>>>

Geographic Layout techniques are very effective for building overlays with a 
high degree of physical locality. However, we found that in the context of 
community networks it may not be the best choice. Network splits are common due to both, 
hardware malfunction (low-end hardware used) and humman errors during management 
operations (difficulty of operating a highly descentralized network). Because of network 
splits, a perfect locality based on Geographic Layout may lead to entire portions of the DHT ID space inaccessible. 
In this sense, Proximity Routing and Proximity Neighbour Selection provides much better 
reliability since the Node IDs have nothing to do with the geographic location.

@@

We believe that Proximity Neighbour Selection offers the best characteristics for 
deployment on CN. ID space is uniformly distributed over the whole network, making 
it robust, while good enough locality can still be achieved by choosing nearby nodes  
as routing table entries.
